---
title: "ICharkin MSDS 6306 DDS Unit 4 Homework"
author: "Ivan Charkin"
date: "June 2, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data used in the home work come from the fivethirtyeight package https://github.com/rudeboybert/fivethirtyeight


## 1. FiveThirtyEight Data

a. Install the fivethirtyeight package.

```{r eval=FALSE}
install.packages("fivethirtyeight")
```

b. In the listing of Data sets in package 'fivethirtyeight,' assign the eighteenth data set to an object 'df.'

```{r}

## This is 22nd, not 18th dataset
library(fivethirtyeight)
data(package = "fivethirtyeight")
df <- college_recent_grads
head(df)
```

c. Use a more detailed list of the data sets to write out the URL in a comment to the related news story.

```{r}
vignette("fivethirtyeight", package = "fivethirtyeight")
?college_recent_grads
```

d. Using R command(s), give the dimensions and column names of this data frame.

```{r}
dim(df)
colnames(df)
```

## Data Summary

a. Write an R command that gives you the column names of the data frame. Right after that, write one that counts the number of columns but not rows. Hint: The number should match one of your numbers in Question 1d for dimensions.

```{r}
colnames(df)
ncol(df)
```

b. Generate a count of each unique major_category in the data frame. I recommend using libraries to help. I have demonstrated one briefly in live-session. To be clear, this should look like a matrix or data frame containing the major_category and the frequency it occurs in the dataset. Assign it to major_count.

```{r}
major_count <- as.data.frame(table (df$major_category))
names(major_count)[1] = 'major_category'
major_count
```

c. To make things easier to read, enter par(las=2) before your plot to make the text perpendicular to the axis. Make a barplot of major_count. Make sure to label the title with something informative (check the vignette if you need), label the x and y axis, and make it any color other than grey. Assign the major_category labels to their respective bar. Flip the barplot horizontally so that bars extend to the right, not upward. All of these options can be done in a single pass of barplot(). Note: It's okay if it's wider than the preview pane.

```{r}
op <- par(no.readonly = TRUE)
par (mar=c(4,9,2,1), oma = c(2, 5, 0, 0), cex.axis=0.7)
barplot(major_count$Freq,horiz=TRUE, las=1, col=3,
        names.arg=major_count$major_category,  
        main="Majors of recent graduates", xlab="Count", ylab="")
title(ylab = "Majors", line = 8)
par(op)
```

d. Write the fivethirtyeight data to a csv file. Make sure that it does not have row labels.

```{r, eval=FALSE}
write.csv(df, file="c:\\TMP\\538.csv", row.names=FALSE)
```

## Codebook

The link to the GitHub repository for this homework:  
https://github.com/icharkin/ICharkin_MSDS6306_HW


