---
title: "ICharkin_MSDS6306_Homework5"
author: "Ivan Charkin"
date: "June 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

In this question we load a TXT file with names for 2016 into R

```{r}
df <- read.table ("D:\\OneDrive\\SMU\\6306 doing data science\\Unit 5\\yob2016.txt", header = FALSE, sep = ";")
head (df)

id2016<- c("Name", "Gender", "Amount2016")
colnames(df) <- id2016
head (df)
str (df)
summary(df)
```

Now remove an observation with three y's

```{r}
badrow<-grep ("yyy$", df$Name)

badrow

y2016 <- df [-badrow,]
```

## Question 2

In this question we load the second file for 2015 names. Displaying the last 10 rows. 

```{r}
y2015 <- read.table ("D:\\OneDrive\\SMU\\6306 doing data science\\Unit 5\\yob2015.txt", header = FALSE, sep = ",")
id2015 <- c("Name", "Gender", "Amount2015")
colnames(y2015) <- id2015
head (y2015)

tail (y2015, 10)
```

All of the "rare" names start with Z. All of the names have "M" gender.

Now we merge datasets for 2015 and 2016 and in the process eliminate the names which are unique for one specific year. 

```{r}
final <- merge(y2015, y2016, by=c("Name", "Gender"))
head(final)
```

## Question 3

In this question we calculate the amounts for 2015 and 2016 and find 10 most popular names. 

```{r}
final$Total <- final$Amount2015+final$Amount2016
head(final)

finalordered <- final [order (-final$Total),  ]
head(finalordered,10)

as.character (finalordered[1:10,"Name"])
```

Since the clients are interested in girl names, we determine the list of 10 most popular girl names and import them to CSV file

```{r}
finalorderedgirls <- finalordered [finalordered$Gender == "F",]
as.character (finalorderedgirls [1:10,"Name"])

finallist <- finalorderedgirls [1:10, c("Name", "Total")]

write.csv(finallist, file = "D:\\OneDrive\\SMU\\6306 doing data science\\Unit 5\\Final_name_list.txt", row.names = FALSE)

```



## Question 4

The link to the GitHub repository for this homework:  
https://github.com/icharkin/ICharkin_MSDS6306_HW

To generate codebooks the following code was used

```{r eval=FALSE}
#codebook
library(dataMaid)
makeCodebook(df,  replace=TRUE)
makeCodebook(y2015, replace=TRUE)
```